Open-Set Domain Adaptation through Self-Supervision

### 2022-01-14 Report/Paper_OpenSet.tex
Related Work - Self-supervised learning

\textcolor{red}{Not sure if the Sakurada study is relevant to our work}

\textbf{Self-supervised learning}...
\cite{Xu2019}, Komodakis,

\textbf{Domain adaptation} ...
Calucci, Csurka, Pau

\textbf{Rotation-based Open Set}...
\cite{Bucci2020}

- what's been done in the past on this topic
 - Summarise each of the cited references
- Cite some papers about the variations we did
 - other variations which might be interesting (but that we didnt do) - if space
-

>>>>

\textbf{Self-supervised learning} has been a key concept aimed at reducing the need for human labeling of data. It has also created opportunities for the use of data in problems where supervision is not possible \cite{Yaman2020}. Self-supervised learning consists of choosing a self-supervised task (or pretext task) to train alongside the main classification task. One possible self-supervised task is image rotation prediction, which is reported to perform best for visual representation learning \cite{Xu2019, Gidaris2018}. However many options are available, including image-patch based methods \cite{Mundhenk2018, Kim2018}, horizontal flipping \cite{Golan2018}, or by solving jigsaw puzzles \cite{Carlucci2019, Kim2018}.

\textbf{Domain adaptation} ...
Calucci, Csurka, Pau, Zhang2016, Ren2021

\textbf{Rotation-based Open Set}...
\cite{Bucci2020}, center-loss paper
